\documentclass[12pt,letterpaper]{article}
\usepackage[parfill]{parskip}

\begin{document}
\section*{CptS 415 Big Data}
\subsection*{Class Participation - Survey}

\vspace{5mm} %5mm vertical space

\hline

\vspace{5mm} %5mm vertical space

Please read and answer the following questions. Submit the response via Canvas.

1. About yourself: what’s your name, major/department, year in program, advisor (if 
any).

My name is Charles Lambert Nguyen.  I am a Computer Science major who
previously switched from Chemical Engineering.  I will be in the program for
2.5 years by the time I graduate in May 2023.

2. What do you expect to learn from this course and why?

I am expecting to learn more about data pipelining and various forms of
database models.

3. Tell me about any course you have taken on algorithms, databases, linear algebra, 
complexity theory, programming languages.

I have taken most of the courses mentioned except for databases.

4. Have you used MapReduce/Hadoop/Spark system before?

I have heard about MapReduce mentioned briefly in the Data Mining course (CptS
315).  I have heard about Hadoop and Spark but have not used them.

5. Have you used any cloud computing/storage service (e.g., Amazon EC2, Microsoft 
Azure) before?

I have used AWS EC2 once before.

6. Have you conducted projects related with data analytics/processing before? If so, 
use 2-3 sentences to briefly describe the project.

I have done a few assignments/projects as part of the class CptS 315 Data
Mining.  I learned a bit about preparing data, which was a lot more work than
I thought.

7. What’s your favorite/major programming language?

I do not have a favorite programming language, but I have recently written a
code in C# and Javascript.

8. Any other comments / expectations you have for the course? 

None that I can think of.

\end{document}
